General linear Models (STAT6123) Coursework

### 2022-11-23 Draft_final.Rmd
Updating script to add bits that will make sense in r script

```{r,echo=F,fig.align = 'left',fig.width=10,fig.height=4}
#Histogram to examine the expenditure
hist(expend.df$expenditure,breaks = 20,
     xlab = "Total weekly household expenditure (£)",
     main = "Histogram of expenditure")
```
```{r,include=F}
#calculating mean of expenditure
mean.expend <- mean(expend.df$expenditure)
mean.expend

@@

```{r,include=F}
#calculating percent increase

model.p5.increase <- function(initial,increase){
  #values of regression coefficients
  beta_1 <- 3.117180e-03	
  beta_2 <- -1.453272e-06

@@

AIC(lm.log.full)

#Iteratively performing model selection process
drop1(lm.log.full)
#removing lab.force:house.ten will decrease AIC
lm.full.1.deletion <- update(lm.log.full,.~.-lab.force:house.ten)
AIC(lm.full.1.deletion)

@@

AIC(lm.final.model)
```

@@

>>>>

```{r,echo=F,fig.align = 'left',fig.width=10,fig.height=4}
#Histogram to examine the expenditure
hist(expend.df$expenditure,breaks = 20,
     xlab = "Total weekly household expenditure (£)",
     main = "Histogram of expenditure")
```

```{r,include=F}
#calculating mean of expenditure
mean.expend <- mean(expend.df$expenditure)
mean.expend

@@

```{r,include=F}
#finaing mean income
mean(expend.df$income)

#calculating percent increase
model.p5.increase <- function(initial,increase){
  #values of regression coefficients
  beta_1 <- 3.117180e-03	
  beta_2 <- -1.453272e-06

@@

AIC(lm.log.full)
#AIC is 1391.914

#Iteratively performing model selection process
drop1(lm.log.full)
#removing lab.force:house.ten will decrease AIC
lm.full.1.deletion <- update(lm.log.full,.~.-lab.force:house.ten)
AIC(lm.full.1.deletion)
#AIC is 1386.878

@@

AIC(lm.final.model)
# AIC is 1406.732
```

@@

```{r, include=F}
#Finding more precise value of income squared than table provides
options(digits=10)

#estimate of exp regression coefficient
round(exp(tidy(lm.final.model)$estimate[6]),8)
#0.99999896

#lower and upper of 95% CI
round(exp(tidy(lm.final.model)$estimate[6]-1.96*tidy(lm.final.model)$std.error[6]),8)
#0.99999866
round(exp(tidy(lm.final.model)$estimate[6]+1.96*tidy(lm.final.model)$std.error[6]),8)
#0.99999927
```
